The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2017-03-08 manuscript/manuscript.Rnw
document that APOB and AFP are associated in mice

We also compared differences in the \mouse lineage in comparison to
all other lineages using a type-III ANOVA as in the \human analysis,
and found few genes which are highly differentially expressed and are
also associated with adverse pregnancy outcomes. Comparisons between
rodentia (\mouse, \galili, and \carmeli) and all other species using
the mean of each species expression did not indicate any significant
differences (Supplemental \cref{tab:rodentia_lineage_specific}) nor
did the equivalent comparisons between laurasiatheria and all other
species (Supplemental \cref{tab:laurasiatheria_lineage_specific}) and
laurasiatheria and euarchontoglires (Supplemental
\cref{tab:laurasiatheria_euarchontoglires_lineage_specific}).
Additional placenta samples of each species and the collection of the
placentas of additional laurasiatherians may resolve the lack of
significance due to insufficient power.

>>>>

We also compared differences in the \mouse lineage in comparison to
all other lineages using a type-III ANOVA as in the \human analysis,
and found few genes which are highly differentially expressed and are
also associated with adverse pregnancy outcomes, including \ac{APOB}
and \ac{AFP} (Supplemental \cref{tab:mouse_lineage_specific_all}).
Comparisons between rodentia (\mouse, \galili, and \carmeli) and all
other species using the mean of each species expression did not
indicate any significant differences (Supplemental
\cref{tab:rodentia_lineage_specific}) nor did the equivalent
comparisons between laurasiatheria and all other species (Supplemental
\cref{tab:laurasiatheria_lineage_specific}) and laurasiatheria and
euarchontoglires (Supplemental
\cref{tab:laurasiatheria_euarchontoglires_lineage_specific}).
Additional placenta samples of each species and the collection of the
placentas of additional laurasiatherians may resolve the lack of
significance due to insufficient power.
